Open Data, Open Source and Open Standards in chemistry - The Blue Obelisk five years on

### 2011-05-12 paper.tex
Text on BO books

\section*{Other areas of activity}
Web services? XMPP services? (NIH, CDK and ChemSpider)

\subsection*{Getting the message out}

One recent development
that attempts to address this issue was the establishment in Apr 2010 of a
question-and-answer (Q\&A)
website related to Blue Obelisk projects and themes at
http://blueobelisk.shapado.com (see Figure~3). This is a website in the
style of Stack Overflow that encourages high quality answers (and
questions) through the use of a voting system. In the year since it
was established, over
200 users have registered, many of whom had no previous involvement
with the Blue Obelisk, showing that the Q\&A website is a nice complement
to earlier existing channels of communication.

Books (Angel, Egon, OB)

>>>>

\section*{Other areas of activity}

While each Blue Obelisk project has its own website and point of
contact (typically a mailing list), because of the breadth of BO
projects it can be difficult for a newcomer to understand which of
them, if any, can best address a particular problem. To address this
issue, members of the Blue Obelisk established a Question \& Answer
website at http://blueobelisk.shapado.com (see Figure~3). 
This is a website in the
style of Stack Overflow that encourages high quality answers (and
questions) through the use of a voting system. In the year since it
was established, over
200 users have registered, many of whom had no previous involvement
with the Blue Obelisk, showing that the Q\&A website complements
earlier existing channels of communication.

The rise of self-publishing and print-on-demand services has meant
that publishing a book is now as straightforward as uploading to an
appropriate website. Unlike the traditional publishing route where
books with projected low sales volume would be expensive,
websites such as Lulu allow the sale of low-priced books on
chemistry software, and books are now available for purchase
on Jmol~\cite{JmolBook}, the Chemistry Development Kit~\cite{CDKBook}
and Open Babel~\cite{OpenBabelBook}.
